\stdpopsim: a community-maintained standard library of population genetic simulations

### 2019-12-17 popSimManu.tex
added blurb on model limitations

>>>>

The models implemented are currently limited to neutral evolution and to populations 
composed of a finite number of randomly-mating demes. Such models do not reflect 
the complexities of demographic and selective forces affecting real populations. 
However, because they are comparatively simple to specify, easy to simulate, 
and widely use in practice,  they serve as a useful starting point for a 
comprehensive library of population genetics models.
